Methodology for Assessing the State of the Practice for Domain X

### 2020-08-30 StateOfPractice/Methodology/Methodology.tex
updated 'How to Identify the Domain' in Methodology document

\section{How to Identify the Domain} \label{SecIdentifyDomain}
\begin{enumerate}
	\item Needs to be "a community of"/many people using and studying this domain
	\item There needs to be "many" software solutions
	\item There needs to be a user community using these solutions
	\item Must be in the research software scope
	\item Specific enough scope
	\item Must be a well understood domain / mature
\end{enumerate}

>>>>

\section{How to Identify the Domain} \label{SecIdentifyDomain}
\begin{enumerate}	
	\item The domain must fall within the research software scope.
	\item The domain must be specific.
	\item The domain must be well understood.
	\item There must be a community of people studying the domain.
	\item There must to be a variety of software solutions for the domain.
	\item These software solutions must have a user community.
\end{enumerate}
